\documentclass[12pt, oneside]{article}   	
\usepackage{geometry}                		
\geometry{letterpaper}                   		
\usepackage{graphicx}				
\usepackage{amssymb, amsmath}
\usepackage{cite}
\usepackage{color}
\usepackage[normalem]{ulem}



\title{SFWR 3XA3: Problem Statement}
\author{Group 211
		\\ Faisal Jaffer
		\\ Pedram Yazdinia
		\\ Dominik Buszowiecki
		\\ Zayed Sheet
		\\ Due: January 24, 2020
		\\Professor: Dr. Asghar Bokhari
		\\ Lab: L02}
\date{}

\begin{document}
\maketitle

Many people using their camera application on their Android mobile devices encounter issues where a certain functionality may be inaccessible \textcolor{red}{as it is difficult to find, use or simply does not exist.} \sout{This could be because the functionality is difficult to find, use or simply does not exist.} Often, we can see that users tend to prefer external applications such as Snapchat, Instagram and TikTok. \sout{for a camera because of the features and functionalities that make it more accessible towards the user’s needs.} While these external applications each have their own unique feature that can fulfill a specific user requirement, they still do not provide a well rounded solution to the problem. \textcolor{red}{The team is focused on creating a one-stop application that gathers all the desired functionalities of the user.}
\\

OpenCamera is an open source camera application that allows users to capture photos outside of the stock Android camera app by providing a simpler UI. However, this software does not include many of the key functionalities that a user may want from their camera. Our goal is to modify the Open Camera application in a way to entice more users to use the application for all their capturing needs while maintaining a clean user interface. 
\\

The stakeholders include any user that requires accessible features in their camera application, \sout{as well as a clean UI for their day-to-day capturing needs} \textcolor{red}{mostly evolved around young adults and teenagers} . \textcolor{red}{In addition to users, stakeholders include our clinets which in our case consists of Dr. Bokhari and the TAs.} \sout{More specifically, the stakeholders devices are limited to OpenCamera compatible versions of Android (4.0 and later).} \textcolor{red}{The optimal environment for the application requires a Camera Enabled Cell phone, running Android 4.0 or later.}
    

\bibliographystyle{acm}
\bibliography{ref.bib}

\end{document}  